Manual of comparing optimal subsampling with model robust optimal subsampling method for logistic regression (Multivariate Normal distribution)

### 2022-06-25 Manual.Rmd
update title with spelling corrections in manual
output clarification added

>>>>

* In **Identical_r0** for OSMAC Assumed Models there are two forms of outputs, 1) **OSMAC_output_New_x.Rdata** is when optimal sub-sampling probabilities are selected from the re-calculated probabilities of the Data Generating model, 2) **OSMAC_output_Old_x.Rdata** is when optimal sub-sampling probabilities are calculated based on the Assumed model. Throughout the simulation setup the later output is used.
